Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/semantics.tex
get rid of the text walking through qss -- doesn't really fit anymore

Although products and functions are restricted to types at the same world,
$\fut$ allows construction of ``mixed-stage'' products and functions.
For example, quickselect is a function at world \bbonem\ which takes a
$\curr{\rm list} \times \fut\rmint$ (a purely-first-stage list and a
second-stage integer) to a $\fut\rmint$ (a second-stage
computation of an integer).

@@

\crem{blend in the rest of the text in this section:}
%
\texttt{qss} has a more precise type---it is a first-stage function which
takes a $\curr\mathrm{list}$ (an integer list now) and a $\fut\rmint$ (an
$\rmint$ \emph{in the future}), and returns a $\fut\rmint$.

Indeed, we case on the list as usual, and in the \texttt{Cons} branch,
\texttt{partition} it. The \texttt{case} term in \texttt{qSelect} depends
on \texttt{k}, whose type $\fut\rmint$ indicates that it is only available to
second-stage computations. Since \texttt{qss} itself produces a
$\fut\rmint$, the remainder of the function is second-stage code.

The $\next$ wraps a second-stage term of type $\rmint$ (the \texttt{case}
term) as a first-stage term of type $\fut\rmint$ (the result 
of \texttt{qss}). Inside the \texttt{LT} and \texttt{GT} branches, the
$\prev$ unwraps first-stage $\fut\rmint$s (the results of the recursive calls
to \texttt{qss}) as second-stage $\rmint$s. In the \texttt{EQ} branch,
$\pause$ promotes a first-stage $\rmint$ (the head of \texttt{l}) directly to a
second-stage $\rmint$.

>>>>

Although products and functions are restricted to types at the same world,
$\fut$ allows construction of ``mixed-stage'' products and functions.
For example, \texttt{qss} is a function at world \bbonem\ which takes a
$\curr{\rm list} \times \fut\rmint$ (a purely-first-stage list and a
second-stage integer) to a $\fut\rmint$ (a second-stage
computation of an integer).

@@
